Dirk Sliwka

### 2025-03-21 papers.qmd
Update bib

**Managing Skills in Organizations-Evidence from a Field Experiment**<br>

@@

<button onclick="toggleAbstract('abstract-2025-Managing-Skills-in-Organizations-Evidence-from-a-Field-Experiment')" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; background: none; display: inline-block;">Abstract</button>
<div id="abstract-2025-Managing-Skills-in-Organizations-Evidence-from-a-Field-Experiment" style="display:none; border: 1px solid #ccc; padding: 10px; margin-top: 10px;">We study the value of skill management in organizations. In a natural field experiment with 2,582 service technicians, we vary managers’ ability to monitor and manage employee skills. We find that removing managers’ access to hard information on employee skills reduced training intensity, work performance, and job satisfaction. Combining detailed personnel records and survey data, we show that the intervention lowered employee efforts to identify training needs and managerial attention to employee development. In particular, high-skill employees received less training to broaden their skill set and, in turn, performance losses are driven by higher completion times for complex work assignments.</div>

>>>>

**Managing Skills in Organizations - Evidence from a Field Experiment**<br>

@@

<a href="https://docs.iza.org/dp17727.pdf" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; display: inline-block;">  WEB  </a>&nbsp;&nbsp;<button onclick="toggleAbstract('abstract-2025-Managing-Skills-in-Organizations---Evidence-from-a-Field-Experiment')" style="border: 1px solid #007a04; color: #007a04; padding: 1px 8px; text-decoration: none; font-size: 0.7em; background: none; display: inline-block;">Abstract</button>
<div id="abstract-2025-Managing-Skills-in-Organizations---Evidence-from-a-Field-Experiment" style="display:none; border: 1px solid #ccc; padding: 10px; margin-top: 10px;">We study the value of skill management in organizations. In a natural field experiment with 2,582 service technicians, we vary managers’ ability to monitor and manage employee skills. We find that removing managers’ access to hard information on employee skills reduced training intensity, work performance, and job satisfaction. Combining detailed personnel records and survey data, we show that the intervention lowered employee efforts to identify training needs and managerial attention to employee development. In particular, high-skill employees received less training to broaden their skill set and, in turn, performance losses are driven by higher completion times for complex work assignments.</div>
